
 * Write an introductory paragraph explaining the domain/data set (feel free to borrow from the project proposal)
 
Animal Crossing: New Horizons is a game people can play on Nintendo switch consoles. Its recent surge in popularity could provide intriguing trends when categorizing elements within the game. We have chosen to explore the data within villagers, insects, and fish within the game and discover the trends that can be found within these datasets.
 
 * Write a summary paragraph that includes information calculated by your
 summary information function
 
In the villagers dataset, I created five different values that summarized information I deemed important. I chose to find the number of different personality traits that exist in the Animal Crossing game because it would be useful to know what kinds of personality a player can expect from villagers and how to handle that when playing the game. The total number of villagers is another important piece of information because it is useful to know how many villagers are possible for a player can encounter playing the game. Last but not least, he most common favorite song and the least common hobby villagers have are some other key characteristics of villagers that can become helpful when determining the type of villager and the best way to deal with them.
 
 * Render your table and describe pertinent observations found in it
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}

Insects <- read.csv("https://raw.githubusercontent.com/info201b-2021-aut/final-project-vickiekknight/main/data/insects.csv?token=AV5GB6PTJDSSBO4XXHQCXSDBUG3PG", encoding = "UTF-8")

Villagers <- read.csv("https://raw.githubusercontent.com/info201b-2021-aut/final-project-vickiekknight/main/data/villagers.csv?token=AV5GB6I25KBECUK3IA3OMOTBUGNL2")
villagers <- read.csv("https://raw.githubusercontent.com/info201b-2021-aut/final-project-vickiekknight/main/data/villagers.csv?token=AV4NGSAV4QVAYKS6XWJDRITBUG3VA")

fishdata <- read.csv("https://raw.githubusercontent.com/info201b-2021-aut/final-project-vickiekknight/main/data/fish.csv?token=AV5HVQNHAIBXMFXL5OXYBT3BUGF7E")

library(ggplot2)
library(readxl)
library(tidyverse)
library(dplyr)
``` 

```{r echo=FALSE}
summary_table <- function(dataset) {
  summary_dataset <- dataset %>%
    group_by(Species) %>%
    rename("Color" = "Color.1") %>%
    select(Species, Name, Gender, Personality, Hobby, Birthday, Favorite.Song) %>%
    mutate(Character.type = paste(Personality, Hobby, sep = ", "))
  return(summary_dataset)
}

villagers <- summary_table(villagers)
```
 
 * Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart


```{r echo=FALSE}
#River Fish

riverFish <- fishdata %>%
  select(Sell, Where.How) %>%
  filter(Where.How == "River") %>%
  arrange(Sell) %>%
  mutate(riverFish, River = Sell) %>%
  select(River) %>%
  sum(riverFish)
  
#Pond Fish

pondFish <- fishdata %>%
  select(Sell, Where.How) %>%
  filter(Where.How == "Pond") %>%
  arrange(Sell) %>%
  mutate(pondFish, Pond = Sell) %>%
  select(Pond) %>%
  sum(pondFish)

#Sea Fish

seaFish <- fishdata %>%
  select(Sell, Where.How) %>%
  filter(Where.How == "Sea") %>%
  arrange(Sell) %>%
  mutate(seaFish, Sea = Sell) %>%
  select(Sea) %>%
  sum(seaFish)

PriceAll = seaFish + pondFish + riverFish

pondFish / PriceAll
riverFish / PriceAll
seaFish / PriceAll

pie(riverFisPriceAllpie(riverFish, pondFish, seaFish))

prices <- c(48840, 137860, 232900)
lbls <- c("Pond Fish", "River Fish", "Sea Fish")
pct <- round(prices/sum(prices)*100)
lbls <- paste(lbls, pct)
lbls <- paste(lbls, "%", sep="")
pie(prices,labels = lbls,
    col = rainbow(length(lbls)),
    main="Chart of Fish Price Diversification")
```

The first Chart is about comparing the prices of different types of fish. 


```{r echo=FALSE}
p <- ggplot(Insects, aes(x = Sell)) + 
  geom_histogram(aes(y=..density..), color="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666")

p

p+ geom_vline(aes(xintercept=mean(Insects)),
                   color="red", linetype = "dashed", size = 1)
```
                   

The second chart is about the insects price population density histogram chart. This chart shows us what is the common sell price for most of the insects. 


```{r echo=FALSE}
ggplot(Villagers, aes(Personality,
       fill = Personality)) + 
  geom_bar()
```

The third chart is about the villagers personality count bar chart. This char shows us the population of the each personality. 
